---
title: "STAT451 PRESENTATION"
author: "Jessica Brungard"
date: "11/2/2021"
output: html_document
---

# BACKGROUND INFORMATION

Creating word clouds from tweets by Donald Trump with tm package and wordcloud2 package

```{r, message =FALSE}
library(RColorBrewer)
library(wordcloud2)
library(tidyverse)
library(tm)
```

```{r}
data <- read.csv('trump_tweets.csv')
```

## Creating our corpus

We use a simple corpus (see help: Simple Corpora)

```{r, warning = FALSE}
# Create a vector containing text column
tweet_corpus <- SimpleCorpus(VectorSource(data$text))

# Now we have a corpus containing 1984 documents 
# Each document represents a Trump Tweet
tweet_corpus
```

## Cleaning our Corpus

```{r, warning = FALSE}
# cleaning the corpus
clean_corpus <- tweet_corpus %>%
  tm_map(removeNumbers) %>%
  tm_map(removePunctuation) %>%
  tm_map(stripWhitespace) %>%
  tm_map(removeWords, stopwords("english")) %>%
  tm_map(content_transformer(tolower))

clean_corpus <- tm_map(clean_corpus, removeWords, words = c("...", "'s", '“',"_"))
```

## Turning our Corpus into a dataframe

```{r}
dtm <- TermDocumentMatrix(clean_corpus) 
matrix <- as.matrix(dtm) 
words <- sort(rowSums(matrix),decreasing=TRUE) 
df <- data.frame(word = names(words),freq=words)
```

## Creating our wordcloud

We are looking at almost 7k words+ which will occur over 16k times. For illustrative purposes, we will create a wordcloud anyway.

```{r}
library(wordcloud2)

# wordcloud with default arguments
wordcloud2(df)

# color and size modification
wordcloud2(df, size=.7, color = 'random-light', background ='grey')

# shape and size modification
wordcloud2(df, size = .7, shape = "pentagon")
```

## More Cleaning

```{r}
# filter for significant frequencies
df2 <- filter(df, freq >= 10)

# remove row containing "..."
df2 <- df2[-c(2),]
```

## More Word Clouds (post cleaning)

```{r}
# color and background color
wordcloud2(df2, color = "random-light", backgroundColor = "grey")

# modifying rotation 
wordcloud2(df2, size = 1, minRotation = -pi/2, maxRotation = -pi/2)

# rotation ratio is the probability of a word rotating (see w/ and w/o)
wordcloud2(df2, size = .9 , minRotation = -pi/6, maxRotation = -pi/6, rotateRatio = 1)

# demonstrate color vector
wordcloud2(df2, color = ifelse(df2[, 2] >= 36, 'red', 'skyblue'))
```

## File Figure Mask and Letter Cloud

See link for known issues regarding silent fail 
<https://github.com/Lchiffon/wordcloud2/issues/12>

```{r}
figPath = system.file("examples/t.png",package = "wordcloud2")
wordcloud2(df2, figPath = figPath, size = .7,color = ifelse(df2[, 2] >= 50, 'red', 'skyblue') ,backgroundColor='grey')
```

```{r}
letterCloud(df, word = "TRUMP", wordSize = .5)
```
